Trending assessment for nowcasts, measurements, and forecasts

### 2024-03-03 paper.tex
Improve Chapter on Trending, exclude notation

%%% --- Mathematics
\usepackage{amsmath,amsfonts,amssymb,amsthm,mathtools, mathabx}
\usepackage{bm} % bold mathematics
\usepackage{bbm} % for blackboard 1
\usepackage[linesnumbered,lined,algo2e,figure,boxed]{algorithm2e}
\usepackage[short]{optidef} % for aligning linear programs

@@

\newcommand{\diffxl}{\mathbf{x}^{\Delta,l}}
\newcommand{\diffyl}{\mathbf{y}^{\Delta,l}}
\newcommand{\diffx}{\mathbf{x}^{\Delta}}
\newcommand{\diffy}{\mathbf{y}^{\Delta}}
\newcommand{\diffxrv}{X^{\Delta}}
\newcommand{\diffyrv}{Y^{\Delta}}
\newcommand{\diffxlt}{\mathbf{x}^{\Delta,l}_t}
\newcommand{\diffylt}{\mathbf{y}^{\Delta,l}_t}
\newcommand{\diffxt}{x^{\Delta}_t}
\newcommand{\diffyt}{y^{\Delta}_t}

@@

\section{Application areas and Notation} \label{sec:notation}
\input{sections/02-notation}

@@

\section{Application to real-world data} \label{sec:application}
\todo{Adjust heading; add introduction to section}
\input{sections/04-application}

@@

\appendix
\section{Data generation for Section~\ref{sec:trending}}\label{sec:app-trending-data-generation}
\input{sections/50-appendix-data-generation}

>>>>

%%% --- Mathematics
\usepackage{amsmath,amsfonts,amssymb,amsthm,mathtools, mathabx}
\usepackage{bm} % bold mathematics
\usepackage{bbm} % for blackboard 1
\usepackage[linesnumbered,lined,algo2e,figure,boxed]{algorithm2e}
\usepackage[short]{optidef} % for aligning linear programs
\usepackage{nccmath} % for fleqn environment

@@

\newcommand{\diffxl}{\mathbf{x}^{\Delta,l}}
\newcommand{\diffyl}{\mathbf{y}^{\Delta,l}}
\newcommand{\diffx}{\mathbf{x}^{\Delta}}
\newcommand{\diffy}{\mathbf{y}^{\Delta}}
\newcommand{\diffxrv}{X^{\Delta}}
\newcommand{\diffyrv}{Y^{\Delta}}
\newcommand{\diffxlt}{\mathbf{x}^{\Delta,l}_t}
\newcommand{\diffylt}{\mathbf{y}^{\Delta,l}_t}
\newcommand{\diffxt}[1][t]{x^{\Delta}_{#1}}
\newcommand{\diffyt}[1][t]{y^{\Delta}_{#1}}

@@

%\section{Application areas and Notation} \label{sec:notation}
%\input{sections/02-notation}

@@

\section{Application to measurement, nowcasting, and forecasting data} \label{sec:application}
\input{sections/04-application}

\section{Discussion and Conclusion}\label{sec:conclusion}

\todo{Write conclusion.}

@@

\appendix

\input{sections/50-appendix-data-generation}
